\nonstopmode

\documentclass[]{tukethesis}
%% -----------------------------------------------------------------
%% UTF-8 ENCODING USED. USE PDFLATEX TO COMPILE YOUR DOCUMENTS.
%% -----------------------------------------------------------------
\usepackage{listings}
\usepackage{courier}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline,captionpos=b}
\usepackage[slovak,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cmap}
%% ---- definicia slovenskych uvodzoviek
\chardef\clqq=18 \sfcode18=0
\chardef\crqq=16 \sfcode16=0
\def\uv#1{\clqq#1\crqq}
%% ------------------------------------
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\renewcommand{\refname}{Bibliography}
\renewcommand{\listfigurename}{List of Figures}
\renewcommand{\listtablename}{List of Tables}
\renewcommand{\contentsname}{Contents}
%%
\usepackage{latexsym}
\usepackage{dcolumn} % alignment on a 'decimal point' in tabular mode
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{nicefrac} % nice fractions
\usepackage{upgreek} % e.g. $\upmu\mathrm{m}$ type micrometer (mu)
\usepackage[final]{showkeys}%color%notref%notcite%final
\usepackage[noprefix]{nomencl}
\usepackage{verbatim}
\usepackage{tabularx}
\makeglossary % command to make *.glo file
% \usepackage{parskip}
\usepackage{indentfirst}
% \usepackage{listings}

\usepackage{caption}
\captionsetup[lstlisting]{font={bf,footnotesize}}
\captionsetup[figure]{font={bf,footnotesize}}
%%
%\usepackage[dvips]{graphicx}
%\DeclareGraphicsExtensions{.eps, .mps}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg,.mps}
\graphicspath{{figures/}} % directory for figures
%%
%% numerical citations (vancouer style)
\usepackage[numbers]{natbib}
%%
%% author-year citations (harvard style) -- prefered !!!
%\usepackage{natbib} \citestyle{chicago}
% -----------------------------------------------------------------
%% tlač !!!
\usepackage[pdftex,unicode=true,bookmarksnumbered=true,
bookmarksopen=true,pdfmenubar=true,pdfview=Fit,linktocpage=true,
pageanchor=true,bookmarkstype=toc,pdfpagemode=UseOutlines,
pdfstartpage=1]{hyperref}
\hypersetup{%
baseurl={http://www.tuke.sk/sevcovic},
pdfcreator={pdfLaTeX},
pdfkeywords={Optimization, thesis, writing},
pdftitle={The Optimization of the Thesis Writing},
pdfauthor={Vojtech Riník},
pdfsubject={Bachelor's Thesis}
} 

%% -----------------------------------------------------------------
%% START YOUR THESIS
%% -----------------------------------------------------------------
%%
%% PLEASE SELECT YOUR PREFERED THESIS TYPE
%%
%% A Bachelor's degree is a first degree at college or university
\bachelorthesis{Bachelor's Thesis}
%%
%% A Master's thesis is a second level college or university degree
%\masterthesis{Master's Thesis}
%% -----------------------------------------------------------------
%% Ak praca nema 'podnazov' zakomentujte riadky \subtitle a \podnazov, 
%% alebo polozky nechajte prazdne
\author{Vojtech Riník}
\title{Atmosphere: Concurrency enabled data synchronization platform with HTML5/JS and Cocoa clients}
\subtitle{}
\abstrakte{This thesis describes Atmosphere, a platform that improves user experience of web, mobile and desktop applications by storing remote objects in local database. The first chapters describe the background and state of existing solutions. Next chapters focus on available technologies that could be employed. With this knowledge the thesis proposes a design for the platform. The implementations are described in detail in the next chapter including example applications. The thesis is concluded by comparing Atmosphere to other projects.}
\keywords{Web applications, Cocoa, Synchronization, Real-time applications}
\degree{Bachelor}
\university{Technical University of Košice}
\faculty{Faculty of Electrical Engineering and Informatics}
\facultyabbr{FEI}
\department{Department of Computers and Informatics}
\departmentabbr{DCI}
\fieldofstudy{9.2.1 Informatics}
\studyprogramme{Informatics}
\supervisor{Assoc. Prof. Ing. František Jakab, PhD.}
\consultanta{Ing. Ivan Klimek}
% \consultantb{RNDr.~Marián Čierny, DrSc.}
\dateofsubmission{May. 22. 2012} 
\town{Košice}
\abstrakt{Táto práca opisuje Atmosphere, platformu, ktorá zlepšuje používanie internetových aplikácii tým, že vzdialené objekty ukladá v lokálnej pamäti. Prvé kapitoly opisuju pozadie a stav terajších riešení. Ďalšie kapitoly sú zamerané na dostupné technológie, ktoré by mohli byť využité. S týmito znalostiami práca navrhuje štruktúru platformy. Implementácie a ukážkové aplikácie sú detailne popísané v ďalších kapitolách. Práca je zakončená porovnaním Atmosphere a iných projektov.}
\klucoveslova{Webové aplikácie, Cocoa, Synchronizácia, Aplikácie v reálnom čase}

\begin{document}
\renewcommand\theHfigure{\theHsection.\arabic{figure}}
\renewcommand\theHtable{\theHsection.\arabic{table}}
\bibliographystyle{dcu}
%% input the 'First page of the Thesis'
\firstpage

%% input the 'Title page of the Thesis'
\titlepage

%% input the 'Metadatasheet of the Thesis'
%\metadatasheet

% \errata % begin the 'Errata' 
% Ak je potrebné, autor na tomto mieste opraví chyby, ktoré našiel
% po vytlačení práce. Opravy sa uvádzajú takým písmom, akým je napísaná
% práca. Ak zistíme chyby až po vytlačení a zviazaní práce, napíšeme
% erráta na samostatný lístok, ktorý vložíme na toto miesto. Najlepšie je
% lístok prilepiť\/ \citep{kat}.
% 
% Forma:
% 
% \tabcolsep=10pt
% \begin{table}[!hb]
%   \centering
%   \begin{tabular}{|c|c|c|c|}\hline
% Strana & Riadok & Chybne & Správne \\\hline\hline
% 12 & 6 & publikácia & prezentácia \\\hline
% 22 & 23 & internet & intranet \\\hline
% & & & \\\hline
% & & & \\\hline
%   \end{tabular}
% \end{table}
% \kerrata

\abstrakte % Abstract in English
\abstrakt % Abstract in Slovak
\endabstract % end of the Abstracts page

%% input the 'Assign of the Thesis'
\assignthesis

%% input the 'Declaration' of the author
\declaration
% I hereby declare that this thesis is my own work and effort. Where
% other sources of information have been used, they have been
% acknowledged.
%%
% Niektorí autori metodických príručiek o~záverečných prácach sa
% nazdávajú, že takéto vyhlásenie je zbytočné, nakoľko povinnosť
% vypracovať záverečnú prácu samostatne, vyplýva študentovi zo zákona
% a na  autora práce sa vzťahuje autorský zákon.

\acknowledgement % begin the 'Acknowledgement'
I would like to thank my supervisor Assoc. Prof. Ing. František Jakab, PhD. and my consultant Ing. Ivan Klimek. I would also like to thank my friends at Relevance, Inc. where the work on Atmosphere was started during open-source fridays. Lastly I would like to thank my family for always supporting me in achieving my goals.
\endacknowledgement

\preface % begin the 'Preface'
The world is online. There is hardly any computer program left that doesn’t utilize the global network. 

When the data is stored somewhere else, there is a new challenge: How to hide this fact from the user? In most cases it is not hidden at all, it is obvious that data is somewhere else. Users have to wait seconds for data to load before being able to interact with them.

There are better solutions though. One example is Google Mail. When user opens Google Mail, the unread messages are downloaded from the server, so when user decides to read them, they can see the contents instantly, without having to wait. This smart idea costs little work and causes a great effect on the user experience.

Atmosphere is a platform that hides networking, like Google Mail does. When an Atmosphere-powered application is used, it seems like the data is on the same computer, which makes using the application much better an experience.

Atmosphere was built along with this thesis, and this thesis describes many aspects of designing, implementing and using Atmosphere.
\endpreface

\thispagestyle{empty}
\tableofcontents
\newpage

\thispagestyle{empty}
%\addcontentsline{toc}{section}{\numberline{}List of Figures}
\listoffigures
\newpage

\thispagestyle{empty}
\addcontentsline{toc}{section}{\numberline{}List of Tables}
\listoftables
\newpage

% \thispagestyle{empty}
% \addcontentsline{toc}{section}{\numberline{}List of Symbols and Abbreviations}
% \printglossary % input the 'List of Symbols and Abbreviations'
% \newpage

% \addcontentsline{toc}{section}{\numberline{}List of Therms}
\listofterms % begin the 'List of Therms'

\begin{description}
\item[HTTP] Hypertext Transfer Protocol
\item[PaaS] Platform as a service, a type of cloud solution
\item[REST] Representational state transfer
\item[SaaS] Software as a service, a type of cloud solution
\end{description}

\setlength{\parindent}{1cm} 
\setlength{\parskip}{0cm}

\endlistofterms
%
\include{introduction}
%
\include{background}

\include{motivation}

\include{technologies}

\include{design}

\include{implementation}

\include{cases}

\include{others}

%
%\include{analytical}
%
%\include{mainpart}
%
\include{conclusion}

\include{bibliography}
%
% \ititnclude{appendixc}
%% begin the 'Curriculumvitae' of the author
% \curriculumvitae\protect\label{page:posledna}
% Táto časť\/ je nepovinná. Autor tu môže uviesť\/ svoje biografické
% údaje, údaje o~záujmoch, účasti na~projektoch, účasti na~súťažiach,
% získané ocenenia, zahraničné pobyty na~praxi, domácu prax, publikácie
% a~pod.
% \endcurriculumvitae

\end{document}
%%