\renewcommand{\thesection} {\Alph{section}}
\setcounter{section}{1}
\section{System guide}

\subsection{JavaScript library}

All of the following sources are available in the \href{https://github.com/vojto/atmos2}{GitHub repository of Atmosphere}.

\subsubsection{AppContext}

\subsubsection*{Pubic Methods}
\item
\textbf{exists}
Check if object exists.
\item
\textbf{updateOrCreate}
Updates or creates object with passed data.
\item
\textbf{create}
Creates new object.
\item
\textbf{update}
Updates object with data.
\item
\textbf{changeID}
Changes ID of an object.
\item
\textbf{relation}
Sets up relationship for an object.
\item
\textbf{objectAtURI}
Returns object at passed URI.
\item
\textbf{dataForURI}
Returns data for object at passed URI.
\item
\textbf{dataForObject}
Returns data for object.
\item
\textbf{objectURI}
Returns URI of an object.
\item
\textbf{allURIs}
Returns URIs of all objeccts.
\item
\textbf{destroy}
Destroy object.
\subsubsection*{Private Methods}
\item
\textbf{\_modelForURI}
Returns model for URI.

\subsubsection{MessageClient}
\subsubsection*{Pubic Methods}
\item
\textbf{connect}
Connects the client.
\item
\textbf{close}
Closes the connection.
\item
\textbf{socketDidClose}
Callback called when socket closes.
\item
\textbf{send}
Sends a message.
\item
\textbf{parseNotification}
Parses incoming notification.
\item
\textbf{parseUpdate}
Parses incoming update notification

\subsubsection{MetaContext}
\subsubsection*{Pubic Methods}
\item
\textbf{configure}
Configures meta context.
\item
\textbf{markURIChanged}
Marks object at URI as changed.
\item
\textbf{findOrCreateObjectAtURI}
Finds or creates meta object for URI.
\item
\textbf{objectAtURI}
Returns meta object for URI.
\item
\textbf{createObjectAtURI}
Creates new meta object for URI.
\item
\textbf{saveObject}
Saves meta object.
\item
\textbf{deleteObject}
Deletes meta object.
\item
\textbf{changeIDAtURI}
Changes ID of meta object for URI.
\item
\textbf{isURILocalOnly}
Returns true if object at URI has flag of being local only.
\item
\textbf{isURIChanged}
Returns true if object at URI has flag of being changed.
\item
\textbf{changedObjects}
Returns all changed objects.
\item
\textbf{markURISynced}
Marks object at URI as synced. (Removes the flag of being changed.)

\subsubsection{ResourceClient}
\subsubsection*{Pubic Methods}
\item
\textbf{fetch}
Fetches remote items.
\item
\textbf{updateFromItems}
Updates local storage from remote JSON object.
\item
\textbf{updateFromItem}
Updates local object from remote JSON object.
\item
\textbf{itemsFromResult}
Extracts items from JSON result.
\item
\textbf{save}
Saves object remotely.
\item
\textbf{execute}
Executes requests against remote service.
\item
\textbf{request}
Creates remote request.
\item
\textbf{ajax}
Makes AJAX call.
\item
\textbf{addHeader}
Adds header to be sent with every HTTP request.

\subsubsection*{Private Methods}
\item
\textbf{\_updateFromData}
Updates local object from data.
\item
\textbf{\_removeObjectsNotInList}
Removes local objects that were not included in the response.
\item
\textbf{\_findPathForObject}
Returns remote path for local object.
\item
\textbf{\_findPathForURI}
Returns remote path for object with URI.
\item
\textbf{\_findPath}
Finds path using routing table.

\subsubsection{Synchronizer}
\subsubsection*{Pubic Methods}

\item
\textbf{constructor}
Constructs synchronizer.
\item
\textbf{bind}
Binds event.
\item
\textbf{trigger}
Triggers event.
\item
\textbf{unbind}
Unbinds event.
\item
\textbf{updateOrCreate}
Updates or create local object with data specified.
\item
\textbf{fetch}
Fetches remote object.
\item
\textbf{save}
Saves local object remotely.
\item
\textbf{execute}
Executes request.
\item
\textbf{request}
Creates request.
\item
\textbf{markObjectChanged}
Marks object as changed.
\item
\textbf{markURISynced}
Marks object as synced.
\item
\textbf{setNeedsSync}
Schedules synchronization for the next cycle.
\item
\textbf{startSync}
Starts synchronization.
\item
\textbf{removeObjectsNotInList}
Removes objects not included in the list passed.
\item
\textbf{setAuthKey}
Sets authentication key.
\item
\textbf{hasAuthKey}
Checks if authentication key is present.
\item
\textbf{didAuth}
Callback for successful authentication.
\item
\textbf{didFailAuth}
Callback for failed authentication.


\subsection{Cocoa library}

The source code for Cocoa library is not included here due to its size. It can be found in \href{https://github.com/vojto/atmos2-cocoa}{GitHub repository of Atmosphere}.

Here follows the documentation for main classes and data structures of Cocoa implementation.

\input{struct___a_t_object_u_r_i}
\input{struct___a_t_route}
\input{interface_a_t_app_context}
\input{interface_a_t_attribute_mapper}
\input{interface_a_t_connection_guard}
\input{interface_a_t_entity_fetch_request}
\input{interface_a_t_mapping_helper}
\input{interface_a_t_message}
\input{interface_a_t_message_client}
\input{interface_a_t_meta_context}
\input{interface_a_t_meta_object}
\input{interface_a_t_object_save_request}
\input{interface_a_t_resource_client}
\input{interface_a_t_synchronizer}
\input{protocol_a_t_synchronizer_delegate-p}